\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2015-12-18 paper/paper.Rnw
More Work

\begin{figure}[htbp]
 \centering
<<results, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE>>=
Turk <- mutate(Turk, plot = ifelse(test_param =="line", "Overlaid Lines", "Scatterplot"), 
               sign=ifelse(correlation > 0, 1, 0), smoothed=ifelse(smoothed=="yes", 1, 0))
#ggplot(data=subset(Turk, smoothed==0), aes(x=correlation, y=percent, colour=plot)) + geom_smooth() + geom_point() + facet_grid(n~.) + scale_colour_discrete(name = "Plot Design") +  labs(title="Unsmoothed Plot Accuracy", y="Percent Correct", x="True Plot Correlation")
ggplot(data=Turk, aes(x=correlation, y=percent, colour=plot)) + geom_smooth(se=F) + geom_point() + facet_grid(n~smoothed) + 
  scale_colour_discrete(name = "Plot Design") + labs(title="Observed Data", y="Percent Correct", x="Correlation") +
  theme(legend.position="bottom")
@
  \label{results}
  \caption{Response accuracy for unsmoothed data, broken by unsmoothed (left), smoothed (right) and sample size. The dots are data points, the lines represent a naive model average fit. Scatter plots generally showed superior performance, with the overlaid line graphs being particularly weak at revealing negative correlation}
\end{figure}

@@

# Need to keep only evaluations done by subject who completed at least 10
x <- data.frame(table(full$subj_id))
keep <- x$Var1[x$Freq>9]
full.sub <- filter(full, subj_id %in% keep)
full.sub$r <- round(full.sub$correlation, 1)
full.sub$rsgn <- ifelse(full.sub$r >= 0, 1, 0)
full.sub$rabs <- abs(full.sub$r)
full.sub$plot <- ifelse(full.sub$test_param == 0, "S", "L")
full.sub <- select(full.sub, subj_id, correct, r, rsgn, rabs, smoothed, n, plot, log_time, response_0, actual_location)#[,c(1,7, 15,16,17,20:26)]
full.sub$attempts <- sapply(strsplit(as.character(full.sub$response_0), ","), length)
full.sub$weights = 1/(full.sub$attempts) #weights are actually number of attempts in the glm
full.sub <- full.sub %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
full.sub$correct <- ifelse(full.sub$response_0 == full.sub$actual_location, 1, 0) #fixing correct for multiple guesses
full.sub$alpha <- log(.05/0.95)
full.sub$subj_id <- as.numeric(full.sub$subj_id)
subsetted <- select(full.sub, rabs, n, alpha, rsgn, smoothed, plot, subj_id, weights, correct)
#write.csv(subsetted, "sas/choices.csv")

@@

\begin{figure}
  \centering
<<residuals, dependson='powerfit', fig.height=4, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE>>=
p1b <- ggplot(data=subset(glmm.resid, plot==1)) + geom_histogram(aes(y=..density.., x=residual)) + labs(title="Scatter plot", x="residual", y=element_blank())
p2b <- ggplot(data=subset(glmm.resid, plot==0)) + geom_histogram(aes(y=..density.., x=residual))+ labs(title="Overlaid Lines", x="residual", y=element_blank())
grid.arrange(p1b, p2b, ncol=2, top = "Residual density plots")
@
  \label{residuals}
  \caption{Histograms of residuals for both the scatter plot (left) and the overlaid lines (right).}
\end{figure}

>>>>

\begin{figure}[htbp]
 \centering
<<results, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE>>=
Turk <- mutate(Turk, plot = ifelse(test_param =="line", "Overlaid Lines", "Scatterplot"), 
               sign=ifelse(correlation > 0, 1, 0), smoothed=ifelse(smoothed=="yes", 1, 0))
#ggplot(data=subset(Turk, smoothed==0), aes(x=correlation, y=percent, colour=plot)) + geom_smooth() + geom_point() + facet_grid(n~.) + scale_colour_discrete(name = "Plot Design") +  labs(title="Unsmoothed Plot Accuracy", y="Percent Correct", x="True Plot Correlation")
ggplot(data=Turk, aes(x=correlation, y=percent, colour=plot)) + geom_smooth(se=F) + geom_point() + facet_grid(n~smoothed) + 
  scale_colour_discrete(name = "Plot Design") + labs(title="Observed Data", y="Percent Correct", x="Correlation") +
  theme(legend.position="bottom")
@
  \label{results}
  \caption{Response accuracy for unsmoothed data, broken by unsmoothed (left), smoothed (right) and sample size. The dots are data points, the lines represent a naive model average fit. Scatter plots generally showed superior performance, with the overlaid line graphs being particularly weak at revealing negative correlation}
\end{figure}

@@

# Need to keep only evaluations done by subject who completed at least 10
x <- data.frame(table(full$subj_id))
keep <- x$Var1[x$Freq>9]
full.sub <- filter(full, subj_id %in% keep)
full.sub$r <- round(full.sub$correlation, 1)
full.sub$rsgn <- ifelse(full.sub$r >= 0, 1, 0)
full.sub$rabs <- abs(full.sub$r)
full.sub$plot <- ifelse(full.sub$test_param == 0, "S", "L")
full.sub <- select(full.sub, subj_id, correct, r, rsgn, rabs, smoothed, n, plot, log_time, response_0, actual_location, pic_id)#[,c(1,7, 15,16,17,20:26)]
full.sub$attempts <- sapply(strsplit(as.character(full.sub$response_0), ","), length)
full.sub$weights = 1/(full.sub$attempts) #weights are actually number of attempts in the glm
full.sub <- full.sub %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
full.sub$correct <- ifelse(full.sub$response_0 == full.sub$actual_location, 1, 0) #fixing correct for multiple guesses
full.sub$alpha <- log(.05/0.95)
full.sub$subj_id <- as.numeric(full.sub$subj_id)
subsetted <- select(full.sub, rabs, n, alpha, rsgn, smoothed, plot, subj_id, weights, correct)
#write.csv(subsetted, "sas/choices.csv")

@@

\begin{figure}
  \centering
<<residuals, dependson='powerfit', fig.height=4, fig.width=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
p1b <- ggplot(data=subset(glmm.resid, plot==1)) + geom_histogram(aes(y=..density.., x=residual)) + labs(title="Scatter plot", x="residual", y=element_blank())
p2b <- ggplot(data=subset(glmm.resid, plot==0)) + geom_histogram(aes(y=..density.., x=residual))+ labs(title="Overlaid Lines", x="residual", y=element_blank())
grid.arrange(p1b, p2b, ncol=2, top = "Residual density plots")
@
  \label{residuals}
  \caption{Histograms of residuals for both the scatter plot (left) and the overlaid lines (right).}
\end{figure}
